%**********************************************
%Choose appropriate document class:

%For B.Tech ==> \documentclass[BTech]{iiitdmdiss}
%For DD ==> \documentclass[DD]{iiitdmdiss}
%For M.Tech ==> \documentclass[MTech]{iiitdmdiss}

%**********************************************
\documentclass[MTech, hidelinks]{iiitdmdiss}
%\documentclass[DD]{iiitdmdiss}
% \documentclass[BTech]{iiitdmdiss}
\usepackage{times}
\usepackage{tikz}
\usepackage{t1enc}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{fancyhdr}
\usepackage[driverfallback=dvipdfm]{hyperref} % hyperlinks for references.
\usepackage{amsmath} % easier math formulae, align, subequations \ldots

\usepackage{booktabs}

\renewcommand{\headrulewidth}{1pt}
\renewcommand{\footrulewidth}{1pt}

\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title page
%-----------------------------------------------
% Provide all the necessary information here
%-----------------------------------------------
\title{Gender classification using GAIT}
\author{Vimalraj S, E S Sarveswara Rao}
\roll{CS23M1007, CS23M1008}
% \author{Vimalraj S}
% \roll{CS23M1007}
% \author{E S Sarveswara Rao}
% \roll{CS23M1008}
\monthyear{MAY 2024}
\department{Computer Science and Engineering with specialization in Data Science and AI}
\guide{Dr. Rahul Raman}
\guidedesignation{Assistant Professor}
\guidedept{Computer Science and Engineering}
\date{15.05.2024}

%\nocite{*}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Declaration of originality
\declaration

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Certificate
\certificate
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Abstract
\abstract

Gender classification is in high demand because of its
versatility. It can be used as a surveillance system for security. It
can also be used to classify customers in retail establishments. In
this work, we propose a new gender classification technique from
a gait silhouette using observation angle-based GEIs. The system
consists of two main parts: the observation angle classification
model and the gender classification model. The observation angle
classification generates 10 observation angle-based GEIs. The
gender classification model uses angle-based GEIs to predict
gender. The proposed methods perform well with freestyle walks
which contain a viewpoint issue.
\\
\vspace{10pt}
\noindent KEYWORDS: \hspace*{0.5em} \parbox[t]{4.4in}{Gender classification, Gait, Gender recognition, GEI, CNN, Freestyle Walk}


\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table of contents etc.

\begin{singlespace}
\tableofcontents
\thispagestyle{empty}

\listoftables
\addcontentsline{toc}{chapter}{LIST OF TABLES}
\listoffigures
\addcontentsline{toc}{chapter}{LIST OF FIGURES}
\end{singlespace}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abbreviations
\abbreviations

\noindent 
\begin{tabbing}
xxxxxxxxxxx \= xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx \kill
\textbf{GEI}   \> Gait Energy Image\\
\textbf{CNN}   \> Convolutional Neural Network\\

\end{tabbing}

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Notation

\notation
\noindent
\begin{singlespace}
\begin{tabbing}
xxxxxxxxxxx \= xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx \kill
\textbf{$\lambda$}  \> wavelength \\

\end{tabbing}
\end{singlespace}

\pagebreak
\clearpage

% The main text will follow from this point so set the page numbering
% to arabic from here on.
\pagenumbering{arabic}
\pagestyle{fancy}
\fancyhf{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Enter the details of roll number, department and year for Header and Footer
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\fancyhead[l]{\leftmark}
\fancyfoot[r]{\thepage}
\fancyhead[r]{CS23M1007, CS23M1008}
\fancyfoot[l]{Department of CSE, IIITDM Kancheepuram, May 2024}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{Chapter1/chapter1}
\input{Chapter2/chapter2}
\input{Chapter3/chapter3}
\input{Chapter4/chapter4}
\input{Chapter5/chapter5}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Bibliography.

\begin{singlespace}
  \bibliography{References}
\end{singlespace}

\end{document}
